Secontrails plots

### 2022-01-13 R/Secontrails plots.Rmd
Debug scdtrailopening done

secondtrails[[1]] # 'paths'
class(secondtrails[[1]]) # SpatialLines (sp)

secondtrails[[2]] # 'lines' Sert à quoi ??
class(secondtrails[[2]]) # matrix

plot(secondtrails[[3]]) # SmoothedSecondTrails
class(secondtrails[[3]]) # sfc_MULTIPOLYGON

secondtrails[[4]] # TrailsDensity
class(secondtrails[[4]]) # "units" ??? A mettre en numeric !

new_inventory <- secondtrails[[5]] # inventory
class(secondtrails[[5]]) # data.frame

secondtrails[[6]] # CostRasterMean. Sert à quoi ??
class(secondtrails[[6]]) # RasterLayer

@@

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails[[3]]), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails[[1]]), col = "red")

@@

HarvestableUp <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))

@@

Future <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "future"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))

@@

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  geom_sf(data = Future,
          aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

@@

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  geom_sf(data = Future,
          aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = NewInventory_crs, # cuted trees
          alpha = 0.5, fill = "red") +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

>>>>

secondtrails$paths # 'paths'
class(secondtrails$paths) # SpatialLines (sp)

secondtrails$lines # 'lines' Sert à quoi ??
class(secondtrails$lines) # matrix

plot(secondtrails$SmoothedSecondTrails) # SmoothedSecondTrails
class(secondtrails$SmoothedSecondTrails) # sfc_MULTIPOLYGON

secondtrails$TrailsDensity # TrailsDensity
class(secondtrails$TrailsDensity) # "units" ??? A mettre en numeric !

new_inventory <- secondtrails$inventory # inventory
class(secondtrails$inventory ) # data.frame

secondtrails$CostRasterAgg  # CostRasterMean. Sert à quoi ??
class(secondtrails$CostRasterAgg) # RasterLayer

@@

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails$paths), col = "red")

@@

# HarvestableUp <- sf::st_as_sf(
#   dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
#   coords = c("Xutm", "Yutm")) %>% 
#   st_set_crs(st_crs(HarvestablePolygons))

@@

# Future <- sf::st_as_sf(
#   dplyr::filter(NewInventory, LoggingStatus == "future"),
#   coords = c("Xutm", "Yutm")) %>% 
#   st_set_crs(st_crs(HarvestablePolygons))

@@

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails$paths), col = "red") +

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  # geom_sf(data = Future,
  #         aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

@@

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  # geom_sf(data = Future,
  #         aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = NewInventory_crs, # cuted trees
          alpha = 0.5, fill = "red") +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

  scale_colour_manual(values = c("Non-harvestable" = "grey",
                                 "Visible defect" = "pink", "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red", "Future" = "orange",
                                 "Reserve" = "purple", "Probed hollow" = "forestgreen")) +
  labs(color = "Logging status") +
  labs(title = "P6 EFI3 Hollow Fuel")
```
